---
title: "Fars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Package Description

`Fars` package reads and plots in a map data from the Fatality Analysis Reporting System (FARS) 
of the National Highway Traffic Safety Administration

## Load Packages

```{r setup}
library(Fars)
library(maps)
library(dplyr)
```

## Included data

Data files included within the package are:

```{r}
list.files(system.file("extdata", package = "Fars"))
```

## Package Functions

### Function `make_filename`

This function returns file name and path based on the input year

```{r}
yr <- 2014
make_filename(yr)
```

### Function 'fars_read'

This function reads a file provided by the make_filename funtion

```{r}
filename <- make_filename(2013)
fars_read(filename)
```

### Function `fars_read_years`

Function that will be used by the fars_summarize_years function

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This function summarizes yearly accidents data, by year/month.

```{r}
fars_summarize_years(2013:2015)
```

### Function `fars_map_state`

The function displays a state map plot including accidents location
by year

```{r}
state_num <- 51 # Virginia
yr <- 2013
fars_map_state(state_num, yr)
```
